\section{General description}
	Designing and manipulating efficient data structures is at the foundation of computer programming. 
	These data structures solve complex problems through well-known, highly difficult techniques that would simply take too long to rediscover from scratch. When faced with certain classes of issues, lack of knowledge of algorithms and data structures might significantly impact a programmer's ability to tackle a given problem. \\	
	In this course we are going to explain some of the most popular data structures used in a variety of scenario's encountered in practice when dealing with structuring and traversal of data. 
	We will also cover the principal pathfinding algorithms, which are extensively used for example in GPS devices, routers, etc.  \\

	\subsection{Relationship with other teaching units}
		This course builds upon the development courses of the first year.	\\		

		Advanced data structures presented in this course are used in the optimization of RDBMS's and are informally presented during INFDEV03-5. They play a role in data analysis, simulations, optimization of code, and many others. \\
		
		Knowledge acquired through the algorithms course is also useful for some of the projects. A word of warning though: projects and development courses are largely independent, so some things that a student learns during the development courses are not used in the projects, some things that a student learns during the development courses are indeed used in the projects, but some things done in the projects are learned within the context of the project and not within the development courses.
