\section{Assessment}
	The course is tested with two exams: a practical examination and a theoretical examination. The final grade is determined by the practical examination. However, to receive the grade in the practical examination you \textbf{must} have a sufficient (i.e. $\geq$ 5.5) grade in the theoretical examination.

	\subsection{Theoretical examination}
		The theoretical examination consists of a \textbf{written exam} which covers the topics seen in class. The questions will be both theoretical and about code analysis, such as understanding what a code snippet does, determining its complexity, or finding mistakes in it.
		The exam lasts two lesson hours (100 minutes). No help is allowed during the exam.\\
		A template of the exam can be found in Attachment 1.

	\subsection{Practical examination}
	The practical examination is a \textbf{programming assignment}, accompanied by a brief \textbf{oral check} (to verify the authorship of code). In the practical assignment, some of the data structures and algorithms seen in class will have to be implemented and applied to a specific case study.\\ 
	A detailed description of the practical assignment can be found in Attachment 2.
%	Important notes:
%	\begin{itemize}
%	\item The assignment must be done individually.
%	\item You must upload your project on Github and (only at the end) on N@tschool. The teachers must be added to the Github repository. 
%	\item Each exercise of the practical assignment is associated to a specific deadline. The intermediate deadlines will be checked through the commits in Github.
%	\item There will be oral checks to verify the authorship of code.
%	\item The framework for the assignment comes only for .NET languages: allowed languages are C\# and F\#.
%	\end{itemize}
	
	\subsection{Retake (herkansing)}
	If one part of the assessment is not sufficient (theoretical and/or practical examination), then you can repeat that part in the following block:
	\begin{itemize}
	\item In week 10 of the following block you can repeat the written exam.
	\item The deadline for the delivery of the practical examination is at the end of week 9 of the following block.
	\end{itemize}
	
